---
title: "A4 Task2 Exploratory Report"
author: "Caitie Reza"
date: "11/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(janitor)
library(here)
library(psych)
library(ggbeeswarm)
```

### Introduction

In this document, I will be using data from the Bonanza Creek Experimental Forest Long Term Ecological Research (LTER) site to explore the counts and sizes of juvenile snowshoe hares, *Lepus americanus*. 

yearly population densities, pellet counts, body size for  across several study sites. 











### Data Analysis
The snowshoe hare data, here named bonanza_hares.csv, is a collection of morphological and population data collected by Knut Keilland, F. Stuart Chapin, Roger Ruess, and Bjorn Flora from 1998 - 2012 at the Bonanza Creek Experimental Forest LTER (see citation below). The dataset consists of *Lepus americanus* sex, age, weight, limb measurements, and individual identification (right and left ear tag) information.   Trap data was used from 3 study sites characterized by habitat type and disturbance level, including bonbs (Bonanza Black Spruce), bonmat (Bonanza mature), and bonrip (Bonanza Riparian). 



Kielland, K., F.S. Chapin, R.W. Ruess, and Bonanza Creek LTER. 2017. Snowshoe hare physical data in Bonanza Creek Experimental Forest: 1999-Present ver 22. Environmental Data Initiative. 




### Exploratory Findings

##### Read In
Before doing anything else, I will read in the snowshoe hare data (bonanza_hares.csv)



```{r}
hare_data <- read_csv(here("data", "bonanza_hares.csv"))
```


#### i) Annual Juvenile Hare Trap Counts
Here, I will make a subgroup showing year and juvenile hare trap counts called "annual_traps".  First, I'll need to only keep observations for juvenile hares, or the "j" entries in the age column. Then, I'll reformat the dates using the date() function of lubridate. 

Then, I'll create a figure plotting trap counts by year. 


```{r}
annual_traps <- hare_data %>% 
  filter(age == "j") %>% 
  mutate("date_new" = mdy(date),
         "year" = year(date_new)) %>%
  group_by(year) %>% 
  count()

ggplot(data = annual_traps, aes(x = year, y = n, fill = "salmon")) + geom_col(position = "dodge") +
  theme_minimal() +
  labs(x = "Year", y = "Total Hares Trapped",
       title = "Fig 1. Annual Juvenile Snowshoe Hare Trap Counts at Bonanza Creek LTER from 1999 - 2012",
       subtitle = "Data from 3 Study Sites in Bonanza Creek Experimental Forest Long Term Ecological Research Site (Kielland, K. et. al, 2017) ", 
       fill = "Study Site") +
  theme(legend.position = "none")
         
         
```

###### **Figure 1.** 
This figure shows the annual trappings for juvenile snowshoe hares across all three Bonanza Creek study sites from 1998 - 2012. 




##### Fig. 1 Takeaways
The distribution is left-skewed, with most annual trappings occurring towards the beginning of this time range (maximum of 126 trappings in 1999) and decreasing with time (minimum of 5 in 2007). On average, 31.5 juvenile hares were trapped each year with a standard deviation of 35.88. In the future, it might be helpful to divide observations by the amount of time or trapping effort in order to standardize the population counts. 




#### ii) Visualizing Hare Weights
Here, I will visualize the relationship between sex and weight of juvenile snowshoe hares trapped at each study site at the Bonanza Creek LTER. First, I'll create a subset of data from hare_data showing only juvenile hares, weight, sex, and site. Then, I will plot weight against 



```{r}
sex_weight <- hare_data %>% 
  filter(age == "j") %>%
  select(sex, age, weight, grid)


ggplot(data = sex_weight, aes(x = sex, y = weight, na.rm = TRUE)) +
  geom_beeswarm(aes(color = grid)) +
  facet_wrap(~grid) +
  geom_boxplot(alpha = .7) +
  labs(x = "Sex", y = "Weight ()",
       title = "Figure 2. Sex and Weight of Juvenile Snowshoe Hare",
       subtitle = "Data from 3 Study Sites in Bonanza Creek Experimental Forest Long Term Ecological Research Site (Kielland, K. et. al, 2017)")



```
###### **Figure 2.** 
This figure shows the relationship between the weight and sex of juvenile snowshoe trapped at three Bonanza Creek LTER study sites from 1998 - 2012. 




##### Figure 2. Takeaways
FILL IN HERE








#### iii) Juvenile Weight Comparison
Now, I will create a finalized table containing summary statistics comparing male and female populations of snowshoe hares by weight and study site. 




**Figure 3.** shows the mean, standard deviation, and sample size for male and female juvenile snowshoe hares from 3 locales in the Bonanza Creek LTER site.  



```{r}

```











